---
title: "Andrew Gilliland's CV"
author: Andrew Gilliland
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "asis", 
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

library(tidyverse)
library(readxl)
library(magick)
library(glue)
library(janitor)
library(bib2df)

source("formatEmploymentHistoryFn.R")

```

```{css, echo=FALSE}
.pagedjs_page:not(:first-of-type) {
--sidebar-width: 0rem;
--sidebar-background-color: #ffffff;
--main-width: calc(var(--content-width) - var(--sidebar-width));
--decorator-horizontal-margin: 0.2in;
}
```

# Aside

```{r logo, warning = FALSE, message = FALSE, error = FALSE, fig.align = "center", out.width="50%"}
logo <- image_read("hex-andygilly.png")
logo
```

## Contact {#contact}

-   <i class="fa fa-link"></i> [andygilly.netlify.app/](https://andygilly.netlify.app/)
-   <i class="fa fa-github"></i> [\@andrewgilly](https://github.com/andrewgilly)
-   <i class="fa fa-linkedin"></i> [\@andygilly](https://linkedin.com/in/andygilly)
-   <i class="fa fa-envelope"></i> [andrewjgilliland\@gmail.com](mailto:andrewjgilliland@gmail.com){.email}
-   <i class="fa fa-phone"></i> (+44)7450 826 083

##  {#skills}

**Programming:**

-   R | R Shiny | R Markdown
-   Tidyverse
-   Blogdown | Bookdown | Pagedown
-   Azure DevOps
-   Jira
-   Confluence
-   Git | GitHub | GHE

**Other IT & Systems:**

-   Prophet Professional 
-   Prophet Enterprise
-   Excel
-   VBA

**Personal interests:**

-   Mountain biking
-   Hill running
-   CrossFit
-   Badminton

## Disclaimer {#disclaimer}

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`

# Main

## Andrew Gilliland {#title}

### Actuarial Model Developer | R Developer

I am an R Developer at [**Hymans Robertson**](https://www.hymans.co.uk/), specialising in the development of R Shiny apps.

I have worked a variety of roles within the actuarial space including modelling & model development, bulk annuity pricing and asset & liability management. More recently I have been gaining experience within pensions & investments.

I am experienced with the end-to-end software development cycle from scoping & design, testing & development, and delivery & release activities. I have a particular enthusiasm for improving the user experience and always looking for better ways to structure a process or present some data.

I'm a very self-driven individual known for being passionate, curious and always open to fresh challenges. I enjoy collaborative work environments where I can learn from my peers, and also share my own knowledge. I'm always open to chat and really enjoy teaching & working with others. 




## Education {data-icon="graduation-cap" data-concise="true"}

```{r print-edu}
edu_data <- read_xlsx("data.xlsx", sheet = "education")

edu_data %>% 
  arrange(desc(end)) %>% 
  mutate(id = 1:n()) %>% 
  pivot_longer(
    starts_with('description'),
    names_to = 'description_num',
    values_to = 'description',
    values_drop_na = TRUE
  ) %>% 
  group_by(id) %>% 
  mutate(
    descriptions = list(description)
  ) %>% 
  ungroup() %>% 
  filter(description_num == 'description_1') %>% 
  mutate(
    timeline = ifelse(
      is.na(start) | start == end,
      end,
      glue('{end} - {start}')
    ),
    description_bullets = map_chr(descriptions, ~paste('-', ., collapse = '\n')),
  ) %>% 
  mutate_all(~ifelse(is.na(.), 'N/A', .)) %>% 
  glue_data(
    "### {title}",
    "\n\n",
    "{institution}",
    "\n\n",
    "{loc}",
    "\n\n",
    "{timeline}", 
    "\n\n",
    "{description_bullets}",
    "\n\n",
    "\n\n\n",
  )
```

## Employment {data-icon="suitcase"}

```{r print-emp}

emp_data <- read_xlsx("data.xlsx", sheet = "employment")
employmentHistory <- emp_data %>%
  replace_na(list(end = "present")) %>%
  mutate(uniqueTitle = paste0(title, "_", org, loc)) %>%
  nest(data = -c(org, loc)) 


glue(formatCurrentEmployment(employmentHistory[1,]),
     formatFormerEmployment(employmentHistory[2,], "Actuarial Model Developer"))

```

## Qualifications {data-icon="award"}

```{r print-awds}
awards <- read_xlsx("data.xlsx", sheet = "awards") %>%
  filter(display) %>%
  mutate(display_text = glue("- {award}")) %>%
  group_by(awardingBody) %>%
  summarize(bullets = paste(display_text, collapse = "\n")) %>%
  arrange(awardingBody) %>%
  glue_data(
    "### {awardingBody}",
    "\n\n",
    "{bullets}",
    "\n\n",
    "\n\n\n"
  )

awards

```

